DPIV Analysis and Real Time Implementation

### 2022-12-05 Paper/main.tex
Add block scheme figure to the main file
Starting with the description of the Camera Parameters setting in the DPIV Online Platform Implementation section

@@

\subsection{DPIV Online Platform Implementation}\label{sec:method}

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=1\columnwidth]{images/Platform}
	\centering{\caption{\label{Platoform}System Design and Hardware Platform Realization block schemes }}
\end{figure}

@@

\subsection{DPIV Online Platform Implementation}\label{sec:method}
In this paper, we propose a DPIV online platform implementation for data acquisition and processing. Starting from a pre-existing DPIV platform that works offline, a new version of the same algorithm
that works online has been implemented. ~\fig\ref{Algorithms} shows a schematic of the two implementations. The feature that most diversifies the two algorithms is based on the fact that the offline algorithm works on a video acquired in a moment before the analysis that is carried out.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\columnwidth]{images/DPIV}
	\centering{\caption{\label{Algorithms}Offline and Online algorithms }}
\end{figure}

The first step involves the camera parameters setting, through the following quantities:

\begin{itemize}
	\item \textbf{Pixelsize}: obtained from the camera datasheet.
	\item \textbf{Magnification}: based on the optical components used in the experimental setup.
	\item \textbf{Exposure time}: chosen on the basis of experimental needs.
	\item \textbf{Image gain}: chosen on the basis of experimental needs.
\end{itemize}

Some simulations have been carried out to evaluate camera performances varying the parameters and the results found are listed below:
\begin{itemize}
	\item Increasing the Gain, the acquired image became clearer (see ~\fig\ref{CamPar}) without affecting the framerate.
	\item Increasing the Exposure time the acquired image became clearer (see ~\fig\ref{CamPar}) but this reduces a lot the framerate. 
	\\A compromise between the clarity of the image obtained by increasing the Exposure time and the framerate must be reached.
	\item If the Exposure Time is too small, even increasing the Gain, the image quality is bad.
\end{itemize}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\columnwidth]{images/CameraParameters}
	\centering{\caption{\label{CamPar}Increase in image quality by acting on camera parameters }}
\end{figure}

The major contribution of this algorithm is represented by the acquisition that takes place in online mode through the communication between the CCD camera and MATLAB downloading the \textbf{Windows SDK and Doc. for Scientific Cameras}.
